Supplementary Materials And Methods

### 2020-11-09 Supplementary_mat_met.Rmd
HG18 solved

```{r,  eval=FALSE}
#HG18

#listMarts(host = 'http://may2009.archive.ensembl.org')

ensembl54 <- useMart(biomart='ENSEMBL_MART_ENSEMBL',
                    dataset='hsapiens_gene_ensembl',
                    host='may2009.archive.ensembl.org')
ensembl54 <- useEnsembl(biomart = 'genes', 
                       dataset = 'hsapiens_gene_ensembl',
                       version = 54)
listMarts(host="may2009.archive.ensembl.org")
useMart("ensembl",host="may2009.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
httr_config <- httr::config(ssl_cipher_list = "DEFAULT@SECLEVEL=1")

mart <- useEnsembl(biomart = "ensembl", 
                   dataset = "hsapiens_gene_ensembl", 
                   version = "54")

hg18 <- getBM(attributes = c("ensembl_transcript_id",
                             "ensembl_gene_id",
                             "chromosome_name", 
                             "start_position",
                             "end_position", 
                             "hgnc_symbol", 
                             "entrezgene", 
                             "strand" ), 
              mart = ensembl54)
```

>>>>

```{r,  eval=FALSE}
#HG18
library(biomaRt)

listEnsemblArchives()

#listMarts(host = 'may2009.archive.ensembl.org')

ensembl54 = useEnsembl(host='may2009.archive.ensembl.org', 
                        biomart = "ensembl", 
                         dataset = "hsapiens_gene_ensembl", 
                         mirror = "useast")

hg18 <- getBM(attributes = c("ensembl_transcript_id",
                              "ensembl_gene_id",
                              "chromosome_name", 
                              "start_position",
                              "end_position", 
                              "hgnc_symbol", 
                              "entrezgene_id", 
                              "strand" ), 
                              mart = ensembl54)
